Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 methodology.tex
change the cite for Design Forward Project

We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforwardwebpage} \NOTE{can we get a better cite? done}. Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).

>>>>

We use a trace-driven approach to workload generation, choosing in particular three parallel application traces gathered to represent exascale workload behavior as part of the DOE Design Forward Project~\cite{designforward-traces} \NOTE{can we get a better cite? done}. Specifically, we study communication traces representing the \emph{Algebraic MultiGrid Solver} (AMG), \emph{Geometric Multigrid V-Cycle from Production Elliptic Solver} (MultiGrid) and \emph{Crystal Router MiniApp} (CrystalRouter).
